Grounding the interaction: anchoring situated discourse in everyday human-robot interaction

### 2011-07-15 cover_letter.tex
Addressed comment on consistency of Fig 15 typography

In the following three sections, we try to address separately each of
the concerns of our three reviewers.

@@

\begin{itemize}
\item All reviewer comments regarding citations have been addressed, as suggested by the reviewer,
\item The reviewer's remark on human tendency to explain in a consistent way the world has been added
\item Language issues have been addressed as well.
\end{itemize}

@@

@@

\subsection{``Fig. 15. please make the spelling and the presentation more
consistent''}

>>>>

Several reviewers noted linguistic issues and terminology/typography 
inconsistencies. We have done our best to carefully proof-read the article,
with the help of a native English speaker.

In the following three sections, we address separately each of
the concerns of our three reviewers.

@@

\begin{itemize}
\item All reviewer comments regarding citations have been addressed, following reviewer's suggestions,
\item The reviewer's remark on human tendency to explain in a consistent way the world has been added
\item Language issues have been addressed as well.
\end{itemize}

@@

We thank the reviewer for this input that has been added to the article.

@@

### 2011-07-15 paper_knowledge.tex
Addressed comment about multi-lingual support
Addressed comment on consistency of Fig 15 typography

ORO offers an extended set of methods to process facts at the triples level,
including:
\begin{itemize}
	\item statement (\ie RDF triples) insertion, removal, update,
	\item pattern-based statements removal,
	\item pattern-based queries (for instance, \stmt{ * isOn
	table}, which means ``return me all objects on table'') and filters (for
	instance, \concept{weight < 150.0}),
	\item consistency check, insertion of statements with consistency
	constraint (only if the new fact does not lead to inconsistencies),
	\item fast concept lookup, with multi-lingual support,
	\item standard SPARQL\footnote{{\em SPARQL Protocol and RDF Query Language}, \url{http://www.w3.org/TR/rdf-sparql-query/}} queries.
\end{itemize}

@@

SPARK can be compared to the \emph{Grounded Situation Model} (GSM) introduced
by Mavridis and Roy~\cite{Mavridis2005} in the sense that they both provide an
amodal physical representation of the world used as a mediator between the
sensor space and symbolic models. They have however a different set of
features: while GSM enables representation of time and imaginary objects (whose
existence is hinted by verbal assertions from a human), SPARK offers a richer
3D model that enables the computation of several spatial relationships between
objects and an effective implementation of perspective taking capabilities.

@@

\begin{figure}[!ht]
\centering
	\begin{tabular}{r|p{7cm}}
	\chatN{rosie} & Servus! The Bavarian robot is up and fit! \\
	\chatN{rosie} & What is the name of the WHITE CLUSTER on the TABLE? \\
	\chatN{human} & ``Rosie's mug'' \\
	\chatN{rosie} &\emph{[add \stmt{obj\_01 label "Rosie's mug"}]}\\
				& What kind of object is ``Rosie's mug''? \\
	\chatN{human} & Mug \\
	\chatN{rosie} & \emph{[add \stmt{obj\_01 type Mug}]}\\
			& What is a Mug?\\ 
	\chatN{human} & Tableware\\
	\chatN{rosie} & \emph{[adds \stmt{Mug subClassOf Tableware}. Rosie knows about \emph{Tableware} --it belongs to the common-sense ontology--.}\\
	 & (...) \\
	\chatN{rosie} &  What is the name of the BLACK CLUSTER on the TABLE? \\
	\chatN{human} & ``my\_laptop'' \\
	\chatN{rosie} & What kind of object is ``my\_laptop''? \\
	\chatN{human} & Computer \\
	\chatN{rosie} & What is a Computer? \\
	\chatN{human} & Artifact \\
	\chatN{rosie} & Do you want me to learn more objects? \\
	\chatN{human} & no \\
	\chatN{rosie} & These objects are odd: ``my\_laptop'' \\
	\end{tabular}
	\caption{Transcript of a Jabber session with the robot Rosie.}
	\label{tab|transcript_kimp}
\end{figure}

>>>>

ORO offers an extended set of methods to process facts at the triples level,
including:
\begin{itemize}
	\item statement (\ie RDF triples) insertion, removal, update,

	\item pattern-based statements removal,

	\item pattern-based queries (for instance, \stmt{ * isOn
	table}, which means ``return me all objects on table'') and filters (for
	instance, \concept{weight < 150.0}),

	\item consistency check, insertion of statements with consistency
	constraint (only if the new fact does not lead to inconsistencies),

	\item fast concept lookup, with possible multi-lingual support (through the
	\concept{@lang} XML annotation, labels of concept can be translated, and
	specific translations can be queried for),

	\item standard SPARQL\footnote{{\em SPARQL Protocol and RDF Query
	Language}, \url{http://www.w3.org/TR/rdf-sparql-query/}} queries.

@@

SPARK can be compared to the \emph{Grounded Situation Model} (GSM) introduced
by Mavridis and Roy~\cite{Mavridis2005} in the sense that they both provide an
amodal physical representation of the world used as a mediator between the
sensor space and symbolic models. They have however a different set of
features: while GSM enables representation of time and imaginary objects (whose
existence is hinted by verbal assertions from a human, also called
\emph{presupposition accomodation}), SPARK offers a richer 3D model that
enables the computation of several spatial relationships between
objects and an effective implementation of perspective taking capabilities.

@@

\begin{figure}[!ht]
\centering
	\begin{tabular}{r|p{7cm}}
	\chatN{rosie} & Servus! The Bavarian robot is up and fit! \\
	\chatN{rosie} & What is the name of the white cluster on the table? \\
	\chatN{human} & ``Rosie's mug'' \\
	\chatN{rosie} &\emph{[\stmt{obj\_01 label "Rosie's mug"} added]}\\
				& What kind of object is ``Rosie's mug''? \\
	\chatN{human} & Mug \\
	\chatN{rosie} & \emph{[\stmt{obj\_01 type Mug} added]}\\
			& What is a Mug?\\ 
	\chatN{human} & Tableware\\
	\chatN{rosie} & \emph{[\stmt{Mug subClassOf Tableware} added. Rosie already
	knows about \emph{Tableware} (it belongs to the common-sense ontology), so
	the interaction stops.]}\\
	& (...) \\
	\chatN{rosie} &  What is the name of the black cluster on the table? \\
	\chatN{human} & ``my\_laptop'' \\
	\chatN{rosie} & What kind of object is ``my\_laptop''? \\
	\chatN{human} & Computer \\
	\chatN{rosie} & What is a Computer? \\
	\chatN{human} & Artifact \\
	\chatN{rosie} & Do you want me to learn more objects? \\
	\chatN{human} & no \\
	\chatN{rosie} & These objects are odd: ``my\_laptop'' \\
	\end{tabular}
	\caption{Transcript of a Jabber session with the robot Rosie.}
	\label{tab|transcript_kimp}
\end{figure}
